Discovering Focused Microgenre Communities: Toy example

### 2023-08-03 old_Rmds/05_new-micro-analysis.qmd
A bunch of deleted and moved folders and updated toy example

```{r}
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "mpred.probs.R"))
    bin.var <- function(x) {
      if_else(x == 2, 1, 0)
      }
    dat.pred <- heavy.dat$m %>% 
              mutate(across(starts_with("Heavy"), as.numeric)) %>% 
              mutate(across(starts_with("Heavy"), bin.var)) %>% 
              right_join(demog.dat) 
    pred.res <- mpred.probs("Heavy", dat.pred)
```

```{r}
    plot.dat <- pred.res$probs$Heavy_Metal_1
    p <- ggplot(data = dat,
                mapping = aes(x = cat.labs, y = prob, 
                              fill = var.type, color = var.type, group = var.type))
    p <- p + geom_hline(yintercept = b, color = "red", linewidth = 0.25)
    p <- p + geom_point(size = 2.5)
    p <- p + geom_line(data = con.x, linewidth = 0.75)
    p <- p + geom_segment(data = cat.x,
                          mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs), 
                          alpha = 0.2, linewidth = 1.15)
    p <- p + geom_ribbon(data = con.x, 
                         mapping = aes(ymin = lo, ymax = hi), 
                         alpha = 0.15, linetype = 0)

@@

>>>>

```{r}
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "mpred.probs.R"))
    bin.var <- function(x) {
      if_else(x == 2, 1, 0)
      }
    dat.pred <- heavy.dat$m %>% 
              mutate(across(starts_with("Heavy"), as.numeric)) %>% 
              mutate(across(starts_with("Heavy"), bin.var)) %>% 
              right_join(demog.dat) 
    pred.res <- mpred.probs("Heavy", dat.pred)

@@

```{r}
    plot.dat <- pred.res$probs$Heavy_Metal_1
    p <- ggplot(data = dat,
                mapping = aes(x = cat.labs, y = prob, 
                              fill = var.type, color = var.type, group = var.type))
    p <- p + geom_hline(yintercept = b, color = "red", linewidth = 0.25)
    p <- p + geom_point(size = 2.5)
    p <- p + geom_line(data = con.x, linewidth = 0.75)

    p <- p + geom_ribbon(data = con.x, 
                         mapping = aes(ymin = lo, ymax = hi), 
                         alpha = 0.15, linetype = 0)

### 2023-08-03 old_Rmds/07-new-micro-analysis-for-real.Rmd
A bunch of deleted and moved folders and updated toy example

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(ggplot2)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r Custom Functions}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "plot.preds.R"))
```

```{r}
    a <- demog.dat()
    summary(a)
    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)

    tab_model(res.latin$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-latin.html"))
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
    tab_model(res.metal$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-metal.html"))
    #webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
```

```{r}

    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    p
```
`

>>>>

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(ggplot2)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    library(webshot)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r Loading Custom Functions}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "plot.preds.R"))
```

```{r Microgenre Regression Moldes}
    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
              "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Age-Squared", 
                            "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.metal <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
    res.latin <- genre.reg.mods("Latin", k = 3, xvars = spec)

    tab_model(res.metal$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-metal.html"))
    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))

    tab_model(res.latin$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-latin.html"))
    webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))

```

```{r Microgenre Regression Plots (Age)}
    age.preds <- pred.probs(x = "age.n", res.metal$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -.02,
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-latin.png"), 
              fig = p,
              height = 25, width = 20)

```

```{r}
    res <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)

    tab_model(res$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-genre.html"))
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
    age.preds <- pred.probs(x = "age.n", res$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age.png"), 
              fig = p,
              height = 25, width = 20)
```

### 2023-08-03 qmd/04_microgenre-analysis.qmd
A bunch of deleted and moved folders and updated toy example

```{r Microgenre Regression Moldes}
    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
              "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Age-Squared", 
                            "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.metal <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
    res.latin <- genre.reg.mods("Latin", k = 3, xvars = spec)

    tab_model(res.metal$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-metal.html"))
    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))

@@

```

```{r Microgenre Regression Plots (Age)}
    age.preds <- pred.probs(x = "age.n", res.metal$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -.02,
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-latin.png"), 
              fig = p,
              height = 25, width = 20)

```

```{r}
    res <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)

    tab_model(res$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-genre.html"))
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
    age.preds <- pred.probs(x = "age.n", res$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age.png"), 
              fig = p,
              height = 25, width = 20)
```

>>>>

```{r Microgenre Regression Moldes}
    spec <- c("poly(educ, 2)", "parcoll", "poly(age.n, 2)", 
              "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Age-Squared", 
                            "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)

@@

    tab_model(res.metal$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-metal.html"))
    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
```

```{r Microgenre Regression Plots (Age)}
    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-latin.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.metal$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
              fig = p,
              height = 25, width = 20)
```
`
